SIR Model With Testing Flows and Isolation

### 2020-12-10 codes/ali_test_sir.Rmd
seperating functions

```{r packages, message=FALSE}
library(ggplot2)
library(tidyr)
library(directlabels)
library(latex2exp)
library(rootSolve)

source("SIRfunctions.R")
```

@@

# R0<1:
R0(params=params)
# R0>1:
R0(params=update(params,beta=2))

# check
all.equal(R0(params=params),R02(params=params))
```

Can we recover $R_0=\beta/\gamma$ of the simple SIR? -yes
```{r checkings}
# checking if simple R_0 for SIR can be recovered?
# Case #1: rho=0
all.equal(R0(params=update(params,rho=0)), params[["beta"]]/params[["gamma"]])
# Case #2: 
all.equal(R0(params=update(params,eta_c=1,eta_w=1)), params[["beta"]]/params[["gamma"]])
```

>>>>

```{r packages, message=FALSE}
source("SIRfunctions.R")
```

@@

# R0<1:
R0(params=params)
# R0>1:
R0(params=update(params,beta=2))
# check
all.equal(R0(params=params),R02(params=params))
```

Can we recover $R_0=\beta/\gamma$ of the simple SIR? -yes
```{r checkings}
# checking if simple R_0 for SIR can be recovered?
# Case #1: rho=0
R0_base <-params[["beta"]]/params[["gamma"]]
all.equal(R0(params=update(params,rho=0)), R0_base)
# Case #2: 
all.equal(R0(params=update(params,eta_c=1,eta_w=1)), R0_base)
```
